---
title: "Species data work"
author: "J. L. Couture"
date: "8/13/2021"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,messages=FALSE,warning = FALSE)

```

```{r}

library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)

```

```{r}

capt<-read_csv("data/faoDat/Capture_2021.1.2/CAPTURE_QUANTITY.csv")%>%
  mutate(unCode=as.character(COUNTRY.UN_CODE))%>%
  rename(alph3spp=SPECIES.ALPHA_3_CODE)

countr<-read_csv("data/faoDat/Capture_2021.1.2/CL_FI_COUNTRY_GROUPS.csv")%>%
  select(unCode=UN_Code,ISO3_Code)

spp<-read_csv("data/faoDat/Capture_2021.1.2/CL_FI_SPECIES_GROUPS.csv")%>%
  select(alph3spp=`3A_Code`,Name_En,Scientific_Name)

chn<-capt%>%
  left_join(.,countr)%>%
  left_join(.,spp)%>%
  filter(ISO3_Code=="CHN",
         PERIOD>2009)%>%
  group_by(PERIOD)%>%
  slice_max(order_by = VALUE,n=10)

ggplot(chn,aes(x=PERIOD,y=VALUE,groups=Name_En))+
  geom_line(aes(color=Name_En))+
  theme_bw()

```

***

### Specific species

[Szuwalski et al. 2020](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0227106#pone-0227106-g009) lists a few of the major capture fisheries, which I did a quick search for on [AquaMaps](www.aquamaps.org) to get an idea of distributions. The smallest distributions I saw were the Mauxia shrimp (*Acetes chinensis*) and the Black scraper (*Thamnaconus modestus*), which each appear to range from Northern Japan to the South China Sea. I pulled data for the shrimp because it looks to be limited to shallower waters and thus have a smaller distribution.

Here I am calculating the total range area:

```{r}

acechi<-read_csv("data/acechi_distr.csv")%>%
  rename(lat=`Center Lat`,long=`Center Long`)

ac2b<-acechi%>%
  select(lat,long)%>%
  group_by(lat)%>%
  summarise(maxLong=max(long),
            minLong=min(long))%>%
  # pivot_longer(cols=maxLong:minLong,values_to = "lon",names_to = "nm")%>%
  # select(-nm)%>%
  # filter(long %in% range(long))%>%
  ungroup()
  # add_row(.[1,])%>%
  
ac2c<-bind_rows(ac2b%>%
                  select(lat,lon=maxLong),
                ac2b%>%
                  select(lat,lon=minLong)%>%
                  arrange(desc(lat)))%>%
  add_row(.[1,])%>%
  st_as_sf(coords=c("lon","lat"),crs=4326)%>%
  summarise(geometry=st_combine(geometry))%>%
  st_cast("POLYGON")

# st_area(ac2c$geometry)

```

```{r}

wrld<-ne_coastline(scale = "medium",returnclass = "sf")%>%
  st_transform(crs=4326)

achiArea<-st_area(ac2c)

ggplot()+
  geom_sf(data=wrld)+
  geom_sf(data=ac2c)+
  geom_point(data=ac2b,aes(x=maxLong,y=lat),color="green")+
  geom_point(data=ac2b,aes(x=minLong,y=lat),color="red")+
  # geom_point(data=ac2c,aes(x=lon,y=lat),color="blue")+
  theme_bw()

```

Total range of *A. chinensis* based on these data is `r as.numeric(achiArea)/1000000` km^2^

$$Marine\ aquaculture=2.3x{10}^6\ ha=23,000{km}^2$$

$$\therefore\ ocean\ farms = \frac{23,000\ {km}^2}{4,0000,000\ {km}^2}=0.575\%$$

***

### Thinking about just linear, not including interior

```{r}

ac2b<-acechi%>%
  select(lat,long)%>%
  group_by(lat)%>%
  summarise(maxLong=max(long),
            minLong=min(long))%>%
  # pivot_longer(cols=maxLong:minLong,values_to = "lon",names_to = "nm")%>%
  # select(-nm)%>%
  # filter(long %in% range(long))%>%
  ungroup()
  # add_row(.[1,])%>%
  
ac2c<-bind_rows(ac2b%>%
                  select(lat,lon=maxLong),
                ac2b%>%
                  select(lat,lon=minLong)%>%
                  arrange(desc(lat)))%>%
  add_row(.[1,])%>%
  st_as_sf(coords=c("lon","lat"),crs=4326)%>%
  summarise(geometry=st_combine(geometry))%>%
  st_cast("POLYGON")

# st_area(ac2c$geometry)

```

