---
title: "Ocean acidification projections"
author: "J. L. Couture"
date: "9/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(googledrive)
library(ncdf4)
library(mregions)
library(sf)

```

## OA Data

These data are from a public database and derived by [Jiang et al. 2019](https://www.nature.com/articles/s41598-019-55039-4) at NCEI. 

*Cite as: Jiang, Li-Qing; Carter, Brendan R.; Feely, Richard A.; Lauvset, Siv K.; Olsen, Are (2019). Global surface ocean pH, acidity, and Revelle Factor on a 1x1 degree global grid from 1770 to 2100 (NCEI Accession 0206289). [indicate subset used]. NOAA National Centers for Environmental Information. Dataset. https://doi.org/10.25921/kgqr-9h49. Accessed 22 September 2021.*

```{r oaDat}

datFile<-"data/surfOA.nc"

drive_download("Surface_pH_2010_2100_RCP85.nc",
                   path=datFile,
                   overwrite = TRUE)

oaDat<-nc_open(datFile)

```



```{r pullVars, echo=FALSE}

lon<-ncvar_get(oaDat,"Longitude")
lat<-ncvar_get(oaDat,"Latitude")
ph<-ncvar_get(oaDat,"pH")
mon<-ncvar_get(oaDat,"Month")
year<-ncvar_get(oaDat,"Year")

nc_close(oaDat)

```


```{r}

library(ggmap)
library(viridis)
library(weathermetrics)
library(chron)
library(RColorBrewer)
library(lattice)

# EmpowerDat plotting function

mapCDF<-function(lat,lon,var,title){
  
  titletext <- "title"
  expand.grid(lat=lat[1,],lon=lon[,1])%>%
    mutate(lon=ifelse(lon>180,-(360-lon),lon),
           ph=as.vector(t(var)))%>%
    ggplot()+
    geom_point(aes(x=lon,y=lat,color=ph),size=1)+
    borders("world",colour="black",fill="grey")+
    scale_color_viridis(na.value="white",name="Surface pH")+
    theme(legend.direction = "vertical",legend.position = "right")+
    coord_quickmap()+
    ggtitle(titletext)+
    theme_bw()
  
}

mapCDF(lat,lon,var=ph[,,1,1])

```

```{r}

### animate
library(gganimate)
## convert the array to df
phDf<-NULL

for (i in 1:10){ # iterate over years

  for(j in 1:12){ # iterate over months in a year
    
    tempDf <- expand.grid(lat=lat[1,],lon=lon[,1])%>%
      mutate(lon=ifelse(lon>180,-(360-lon),lon),
             ph=as.vector(t(ph[,,j,i])))%>%
      mutate(month=as.numeric(j),
             year=as.numeric(2000+10*i))
    
  }
  
    phDf = phDf %>% bind_rows(tempDf)
}

phDf<-phDf%>%
  mutate(date=paste(month, year, sep = "/"))

### gganimate


phAnim<-ggplot(phDf,aes(x=lon,y=lat,color=ph),size=1)+
  geom_point()+
  borders("world",colour="black",fill="grey")+
  scale_color_viridis(na.value="white",name="Surface pH")+
  theme(legend.direction = "vertical",legend.position = "right")+
  coord_quickmap()+
  theme_bw()+
  labs(title="Ocean acidification",subtitle = "Year:{current_frame}")+
  transition_manual(year)
  
animate(phAnim)

# anim_save()

```
###### Delete data file from local

```{r}

if (file.exists(datFile)) {
 unlink(datFile)
 cat(paste("The file has been deleted: ",datFile))
}

```

