---
title: "Climate velocities - Revillagigedo MPA"
author: "J. L. Couture"
date: "5/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(googledrive)
library(ncdf4)
library(mregions)
library(sf)
library(ggmap)
library(viridis)
library(weathermetrics)
library(chron)
library(RColorBrewer)
library(lattice)
library(gganimate)
library(lubridate)
library(raster)
library(rgdal)
library(metR)


```

Here CMIP6 projection data will be used to plot ocean temperatures into the future at the Revillagigedo MPA in the eastern Pacific Ocean. The Revillagigedo MPA protects the Revillagigedo Archipelago which is made up of 4 islands ober 500 km from mainland Mexico (Cabo San Lucas). The MPA protects the convergence of 2 ocean currents which make this an important site for several species, including 26 species of endemic fish, and acts as a wintering and calving area for humpback whales. 

## Access CMIP6 ensamble data from oneDrive

These data were ensambled by Isaac Brito Morales and stored on the Conservation International OneDrive for internal access. Data are of sea water potential temperature (K) modeled at several layers of the pelagic:

- epipelagic
- mesopelagic
- bathypelagic
- seafloor

```{r RevillagigedoMPA}

revShp<-st_read("WDPA_WDOECM_Mar2022_Public_555629385_shp/WDPA_WDOECM_Mar2022_Public_555629385_shp_0/WDPA_WDOECM_Mar2022_Public_555629385_shp-polygons.shp")

revBB<-st_bbox(revShp)
buff <- 5

ploArea<-st_bbox(c(xmin=as.numeric(revBB$xmin-buff),
                   xmax=as.numeric(revBB$xmax+buff),
                   ymin=as.numeric(revBB$ymin-buff),
                   ymax=as.numeric(revBB$ymax+buff)),crs = st_crs(revShp))

### isolate base layers

mxShp<-map_data("world",region="Mexico")%>%
  st_as_sf(.,
           coords=c("long","lat"),
           crs="+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")%>%
  group_by(group) %>%
  summarise(geometry = st_combine(geometry)) %>%
  st_cast("POLYGON")%>%
  st_crop(.,ploArea)


# mrRev<-mr_shp(key="MarineRegions:eez",
#              filter="Mexican Exclusive Economic Zone")%>%
#   filter(long > as.numeric(ploArea$xmin),
#          long < as.numeric(ploArea$xmax))%>%
#   filter(lat > as.numeric(ploArea$ymin),
#          lat < as.numeric(ploArea$ymax))

```



```{r getDat-epi}

### read in raster layers and clip to MPA

# raster dimensions are 360 x 720 x 259200 x 1032, likely: lat, lon, ???, month from 2015-2100
# data are temperature potential in Kelvin (will need to convert to Celcius)
# is the several (259200) dimensions depth?


datFile<-"tempDat/cmip6/sstMon.nc"

drive_download("tos_Omon_ACCESS-CM2_ssp126_r1i1p1f1_gn_201501-210012.nc",
                   path=datFile,
                   overwrite = TRUE)

sst<-nc_open(datFile)


### delete large file once the object has been created
if (file.exists(datFileE)) {
 unlink(datFileE)
 cat(paste("The file has been deleted: ",datFileE))
}

```

```{r pullVars, echo=FALSE}

lon<-ncvar_get(sst,"longitude")
lat<-ncvar_get(sst,"latitude")
sstVar<-ncvar_get(sst,"tos") # in degC
timeBnd<-ncvar_get(sst,"time_bnds")
# year<-ncvar_get(sst,"Year")

ttl<-ncatt_get(sst,"tos","long_name")
ttlNm<-as.character(ttl$value)

# datesDf<-tibble(date=as_date(timeBnd[1,],origin="1850-01-01"))%>%
#   mutate(year=year(date))

sstRast<-brick(sstVar,
               xmn=-90,
               xmx=90,
               ymn=-180,
               ymx=180)
names(sstRast)<-paste(rep(c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"),86),rep(2015:2100,each=12))

sstRast2<-t(sstRast)
sstRast3<-flip(sstRast2)

### clip to rev area

sstRev<-crop(sstRast3,ploArea)
names(sstRev)<-paste(rep(c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"),86),rep(2015:2100,each=12))

crs(sstRev) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 

```


```{r}

library(VoCC)
library(repmis)
library(doParallel)

#### Calculating gradient-based velocities around the Revillagigedo MPA

rev_r<-sumSeries(sstRev,p="2020-01/2050-12",yr0="2015-01-01",l=nlayers(sstRev),fun = function(x) colMeans(x, na.rm = TRUE), freqin = "months", freqout = "years")

rev_vt<-tempTrend(rev_r,th=10)

rev_vg<-spatGrad(rev_r,th=0.0001,projected=FALSE)

rev_gv<-gVoCC(rev_vt,rev_vg)

#### Calculating distance-based velocities around the Revillagigedo MPA

rev5<-stack(mean(rev_r[[1:5]],na.rm=TRUE),mean(rev_r[[27:31]],na.rm=TRUE))## this will compare 2020-2025 against 2045-2050

clim<-na.omit(data.frame(getValues(rev5),cid=1:ncell(rev_r)))

clim[,c("x","y")] <- xyFromCell(r,clim$cid)

rev_v<-dVoCC(clim,n=1,tdiff=40,method = "single",climTol = 0.1,geoTol = 20,distfun = "GreatCircle", trans = NA, lonlat = TRUE) # errored, not run

```

```{r}

### plot map of gradient-vel

my.at <- seq(-50, 50, by = 5)
p1 <- rasterVis::levelplot(rev_gv[[1]],  at=my.at, main = 'Gradient-based vocc', margin = FALSE)

```

```{r}

### ggplot of gradient velocities

revGvDf<-as.data.frame(rev_gv,xy=TRUE)


revGvPlt<-ggplot()+
  geom_raster(data=revGvDf,aes(x=x,y=y,fill=voccMag))+
  scale_fill_gradient(limits=c(0,52),low="white",high = "orangered")+
  geom_sf(data = revShp,fill=NA, color="white")+
  geom_sf(data = mxShp,fill="gray33",color="gray33")+
  # scale_x_continuous(expand = c(0,0))+
  # scale_y_continuous(expand = c(0,0))+
  geom_vector(data = revGvDf,aes(x=x,y=y,angle=voccAng,mag=voccMag))+
  ggtitle("Climate velocities (SST)")+
  theme_bw()

revGvPlt

```

