---
title: 'Revillagigedo MPA: Temperature at depth'
author: "J. L. Couture"
date: "3/9/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(googledrive)
library(ncdf4)
library(mregions)
library(sf)
library(ggmap)
library(viridis)
library(weathermetrics)
library(chron)
library(RColorBrewer)
library(lattice)
library(gganimate)
library(lubridate)
library(raster)
library(rgdal)


```

Here CMIP6 projection data will be used to plot ocean temperatures into the future at the Revillagigedo MPA in the eastern Pacific Ocean. The Revillagigedo MPA protects the Revillagigedo Archipelago which is made up of 4 islands ober 500 km from mainland Mexico (Cabo San Lucas). The MPA protects the convergence of 2 ocean currents which make this an important site for several species, including 26 species of endemic fish, and acts as a wintering and calving area for humpback whales. 

## Access CMIP6 ensamble data from oneDrive

These data were ensambled by Isaac Brito Morales and stored on the Conservation International OneDrive for internal access. Data are of sea water potential temperature (K) modeled at several layers of the pelagic:

- epipelagic
- mesopelagic
- bathypelagic
- seafloor

```{r RevillagigedoMPA}

revShp<-st_read("WDPA_WDOECM_Mar2022_Public_555629385_shp/WDPA_WDOECM_Mar2022_Public_555629385_shp_0/WDPA_WDOECM_Mar2022_Public_555629385_shp-polygons.shp")

revBB<-st_bbox(revShp)
buff <- 5

ploArea<-st_bbox(c(xmin=as.numeric(revBB$xmin-buff),
                   xmax=as.numeric(revBB$xmax+buff),
                   ymin=as.numeric(revBB$ymin-buff),
                   ymax=as.numeric(revBB$ymax+buff)),crs = st_crs(revShp))

### isolate base layers

mxShp<-map_data("world",region="Mexico")%>%
  st_as_sf(.,
           coords=c("long","lat"),
           crs="+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")%>%
  group_by(group) %>%
  summarise(geometry = st_combine(geometry)) %>%
  st_cast("POLYGON")%>%
  st_crop(.,ploArea)


# mrRev<-mr_shp(key="MarineRegions:eez",
#              filter="Mexican Exclusive Economic Zone")%>%
#   filter(long > as.numeric(ploArea$xmin),
#          long < as.numeric(ploArea$xmax))%>%
#   filter(lat > as.numeric(ploArea$ymin),
#          lat < as.numeric(ploArea$ymax))

```



```{r getDat-epi}

### read in raster layers and clip to MPA

# raster dimensions are 360 x 720 x 259200 x 1032, likely: lat, lon, ???, month from 2015-2100
# data are temperature potential in Kelvin (will need to convert to Celcius)
# is the several (259200) dimensions depth?

datFileE<-"tempDat/thetaoEpi.rds" #where to put it

drive_download("02-ep_thetao_AEMean_ssp585_r1i1p1f1_2015-2100.rds", #raster file
                   path=datFileE,
                   overwrite = TRUE)

epiT<-read_rds(datFileE) # raster file


### delete large file once the object has been created
if (file.exists(datFileE)) {
 unlink(datFileE)
 cat(paste("The file has been deleted: ",datFileE))
}

```


### testing on one layer 2050

```{r}


### test with one raster layer: Jan 2050
ep50Jan<-epiT[[421]]

ep50jr2<-as(ep50Jan,"SpatialPixelsDataFrame")%>%
  as.data.frame()%>%
  filter(x > as.numeric(revBB$xmin)-buff,
         x < as.numeric(revBB$xmax)+buff)%>%
  filter(y > as.numeric(revBB$ymin)-buff,
         y < as.numeric(revBB$ymax)+buff)

colnames(ep50jr2)<-c("temp","lon","lat")

ggplot()+
  geom_raster(data=ep50jr2,aes(x=lon,y=lat,fill=temp))+
  geom_sf(data = revShp,fill=NA, color="white")+
  geom_sf(data = mxShp,fill="grey",color="black")+
  scale_fill_viridis_c(limits=c(21,27))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  ggtitle("Epipelagic: 2050")+
  theme_bw()

```

```{r}

#### pull 2050 data layers

ep50<-epiT[[421:432]] ### pull just 2050 data

ep50r<-crop(ep50,ploArea)

#### animate the 12 months of 2050 

ep2050<-data.frame()

for(i in 1:nlayers(ep50r)){
  
  tmp<-as(ep50r[[i]],"SpatialPixelsDataFrame")%>%
    as.data.frame()%>%
    mutate(mon=i)
    
  colnames(tmp)<-c("temp","lon","lat","mon")
  
  ep2050<-bind_rows(ep2050,tmp)
  
}

ep2050<-ep2050%>%
  mutate(month=month(mon,label=TRUE,abbr=FALSE))

#### plot

epi2050Plts <- ggplot()+
  geom_raster(data=ep2050,aes(x=lon,y=lat,fill=temp))+
  geom_sf(data = revShp,fill=NA, color="white")+
  geom_sf(data = mxShp,fill="grey",color="black")+
  scale_fill_viridis_c(limits=c(20,32))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  theme_bw()+
  theme(plot.title = element_text(size = 16, face = "bold",hjust = 0.5),
        plot.subtitle = element_text(size=13, color = "blue4",hjust = 0.5))+
  labs(title="2050",subtitle = "{closest_state}")+
  transition_states(month,transition_length = 3)

#### save animated plot

# anim_save(filename = "gifs/potTempEpi2050RevMx.gif")

```

```{r}

#### pull 2015 data layers

ep15<-epiT[[1:12]] ### pull just 2050 data

ep15r<-crop(ep15,ploArea)

#### animate the 12 months of 2050 

ep2015<-data.frame()

for(i in 1:nlayers(ep15r)){
  
  tmp<-as(ep15r[[i]],"SpatialPixelsDataFrame")%>%
    as.data.frame()%>%
    mutate(mon=i)
    
  colnames(tmp)<-c("temp","lon","lat","mon")
  
  ep2015<-bind_rows(ep2015,tmp)
  
}

ep2015<-ep2015%>%
  mutate(month=month(mon,label=TRUE,abbr=FALSE))

#### plot

epi2015Plts <- ggplot()+
  geom_raster(data=ep2015,aes(x=lon,y=lat,fill=temp))+
  geom_sf(data = revShp,fill=NA, color="white")+
  geom_sf(data = mxShp,fill="grey",color="black")+
  scale_fill_viridis_c(limits=c(20,32))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  theme_bw()+
    theme(plot.title = element_text(size = 16, face = "bold",hjust = 0.5),
        plot.subtitle = element_text(size=13, color = "blue4",hjust = 0.5))+
  labs(title="2015",subtitle = "{closest_state}")+
  transition_states(month,transition_length = 3)

# anim_save(filename = "gifs/potTempEpi2015RevMx.gif")

```

```{r}

#### pull 2100 data layers

ep100<-epiT[[1021:1032]] ### pull just 2050 data

ep100r<-crop(ep100,ploArea)

#### animate the 12 months of 2050 

ep2100<-data.frame()

for(i in 1:nlayers(ep100r)){
  
  tmp<-as(ep100r[[i]],"SpatialPixelsDataFrame")%>%
    as.data.frame()%>%
    mutate(mon=i)
    
  colnames(tmp)<-c("temp","lon","lat","mon")
  
  ep2100<-bind_rows(ep2100,tmp)
  
}

ep2100<-ep2100%>%
  mutate(month=month(mon,label=TRUE,abbr=FALSE))

#### plot

epi2100Plts <- ggplot()+
  geom_raster(data=ep2100,aes(x=lon,y=lat,fill=temp))+
  geom_sf(data = revShp,fill=NA, color="white")+
  geom_sf(data = mxShp,fill="grey",color="black")+
  scale_fill_viridis_c(limits=c(20,32))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  theme_bw()+ 
  theme(plot.title = element_text(size = 16, face = "bold",hjust = 0.5),
        plot.subtitle = element_text(size=13, color = "blue4",hjust = 0.5))+
  labs(title="2100",subtitle = "{closest_state}")+
  transition_states(month,transition_length = 3)

# anim_save(filename = "gifs/potTempEpi2100RevMx.gif")

```

```{r}

epi2015Plts + epi2050Plts + epi2100Plts +
  plot_layout(ncol=3,
              guides="collect")

```
## Mesopelagic

```{r getDat-mso}

datFileM<-"tempDat/thetaoMso.rds" #where to put it

drive_download("03-mp_thetao_AEMean_ssp585_r1i1p1f1_2015-2100.rds",
                   path=datFileM,
                   overwrite = TRUE)

msoT<-read_rds(datFileM) 

### delete large file once the object has been created

if (file.exists(datFileM)) {
 unlink(datFileM)
 cat(paste("The file has been deleted: ",datFileM))
}

```


```{r}

#### pull 2050 data layers

ms50<-msoT[[421:432]] ### pull just 2050 data

ms50r<-crop(ms50,ploArea)

#### animate the 12 months of 2050 

ms2050<-data.frame()

for(i in 1:nlayers(ms50r)){
  
  tmp<-as(ms50r[[i]],"SpatialPixelsDataFrame")%>%
    as.data.frame()%>%
    mutate(mon=i)
    
  colnames(tmp)<-c("temp","lon","lat","mon")
  
  ms2050<-bind_rows(ms2050,tmp)
  
}

ms2050<-ms2050%>%
  mutate(month=month(mon,label=TRUE,abbr=FALSE))

#### plot

mso2050Plts <- ggplot()+
  geom_raster(data=ms2050,aes(x=lon,y=lat,fill=temp))+
  geom_sf(data = revShp,fill=NA, color="white")+
  geom_sf(data = mxShp,fill="grey",color="black")+
  scale_fill_viridis_c(limits=c(10,15.5))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  theme_bw()+
    theme(plot.title = element_text(size = 16, face = "bold",hjust = 0.5),
        plot.subtitle = element_text(size=13, color = "blue4",hjust = 0.5))+
  labs(title="2050",subtitle = "{closest_state}")+
  transition_states(month,transition_length = 3)

#### save animated plot

# anim_save(filename = "gifs/potTempMso2050RevMx.gif")

```

```{r}

#### pull 2015 data layers

ms15<-msoT[[1:12]] ### pull just 2050 data

ms15r<-crop(ms15,ploArea)

#### animate the 12 months of 2050 

ms2015<-data.frame()

for(i in 1:nlayers(ms15r)){
  
  tmp<-as(ms15r[[i]],"SpatialPixelsDataFrame")%>%
    as.data.frame()%>%
    mutate(mon=i)
    
  colnames(tmp)<-c("temp","lon","lat","mon")
  
  ms2015<-bind_rows(ms2015,tmp)
  
}

ms2015<-ms2015%>%
  mutate(month=month(mon,label=TRUE,abbr=FALSE))

#### plot

mso2015Plts <- ggplot()+
  geom_raster(data=ms2015,aes(x=lon,y=lat,fill=temp))+
  geom_sf(data = revShp,fill=NA, color="white")+
  geom_sf(data = mxShp,fill="grey",color="black")+
  scale_fill_viridis_c(limits=c(10,15.5))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  theme_bw()+
    theme(plot.title = element_text(size = 16, face = "bold",hjust = 0.5),
        plot.subtitle = element_text(size=13, color = "blue4",hjust = 0.5))+
  labs(title="2015",subtitle = "{closest_state}")+
  transition_states(month,transition_length = 3)

# anim_save(filename = "gifs/potTempMso2015RevMx.gif")

```

```{r}

#### pull 2100 data layers

ms100<-msoT[[1021:1032]] ### pull just 2050 data

ms100r<-crop(ms100,ploArea)

#### animate the 12 months of 2050 

ms2100<-data.frame()

for(i in 1:nlayers(ms100r)){
  
  tmp<-as(ms100r[[i]],"SpatialPixelsDataFrame")%>%
    as.data.frame()%>%
    mutate(mon=i)
    
  colnames(tmp)<-c("temp","lon","lat","mon")
  
  ms2100<-bind_rows(ms2100,tmp)
  
}

ms2100<-ms2100%>%
  mutate(month=month(mon,label=TRUE,abbr=FALSE))

#### plot

mso2100Plts <- ggplot()+
  geom_raster(data=ms2100,aes(x=lon,y=lat,fill=temp))+
  geom_sf(data = revShp,fill=NA, color="white")+
  geom_sf(data = mxShp,fill="grey",color="black")+
  scale_fill_viridis_c(limits=c(10,15.5))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  theme_bw()+
    theme(plot.title = element_text(size = 16, face = "bold",hjust = 0.5),
        plot.subtitle = element_text(size=13, color = "blue4",hjust = 0.5))+
  labs(title="2100",subtitle = "{closest_state}")+
  transition_states(month,transition_length = 3)

# anim_save(filename = "gifs/potTempMso2100RevMx.gif")

```
