---
title: "Testing Spp Distributions"
output:
  html_document:
    code_folding: hide
    fig_width: 12
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE,warning = FALSE)
```

## Aquamaps data

[Aquamaps](https://www.aquamaps.org/) data (managed by the Environmental Markets Lab at UCSB) provides species range data and estimates into the future based on environmental envelopes and projections of changes to ocean conditions. These estimates are limited, so results are to be treated accordingly. The goals here are to 

1. Plot species richness in an area (current)
2. Plot estimates of future species richness (2050)
3. Calculate changes to richness at a site
4. Identify major fisheries in the MPA
5. Highlight changes in major fisheries by 2050

```{r aquamapsData}

### libraries
library(tidyverse)
library(googledrive)
library(sf)
library(kableExtra)
library(patchwork)

### current data
datFileNow<-"tempDat/aquamapsFut.csv" #where to put it

drive_download("rcp85_hcaf_species_native_2050.csv", #csv file, rcp85_hcaf_species_native_2050 (future), hcaf_species_native-001.csv (present)
                   path=datFileNow,
                   overwrite = TRUE)

aqFut<-read_csv(datFileNow)

### delete large file once the object has been created
if (file.exists(datFileNow)) {
 unlink(datFileNow)
 cat(paste("The file has been deleted: ",datFileNow))
}


###temp pull in
# aqNow<-read_csv("tempDat/aquamapsNow.csv",
#                 col_select = c(SpeciesID,CenterLat,CenterLong,Probability))

# aq50<-read_csv("tempDat/rcp85_hcaf_species_native_2050.csv",
#                 col_select = c(SpeciesID,CenterLat,CenterLong,Probability))

```

## Revillagigedo MPA species richness

Revillagigedo MPA

```{r RevMPA}

revShp<-st_read("WDPA_WDOECM_Mar2022_Public_555629385_shp/WDPA_WDOECM_Mar2022_Public_555629385_shp_0/WDPA_WDOECM_Mar2022_Public_555629385_shp-polygons.shp")

revBB<-st_bbox(revShp)
buff <- 7

ploArea<-st_bbox(c(xmin=as.numeric(revBB$xmin-buff),
                   xmax=as.numeric(revBB$xmax+buff),
                   ymin=as.numeric(revBB$ymin-buff),
                   ymax=as.numeric(revBB$ymax+buff)),crs = st_crs(revShp))

### isolate base layers

mxShp<-map_data("world",region="Mexico")%>%
  st_as_sf(.,
           coords=c("long","lat"),
           crs="+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")%>%
  group_by(group) %>%
  summarise(geometry = st_combine(geometry)) %>%
  st_cast("POLYGON")%>%
  st_crop(.,ploArea)

```

```{r}

# aqRev<-aqNow%>%
#   st_as_sf(coords=c("CenterLong","CenterLat"),
#            crs=4326)%>%#"+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")%>%
#   st_crop(ploArea)

### crop current data to Revillagigedo area

# aqRev<-aqNow%>%
#   filter(CenterLong>as.numeric(ploArea$xmin),
#          CenterLong<as.numeric(ploArea$xmax),
#          CenterLat>as.numeric(ploArea$ymin),
#          CenterLat<as.numeric(ploArea$ymax))%>%
#   st_as_sf(coords=c("CenterLong","CenterLat"),
#            crs=4326)
# 
# st_write(aqRev,"data/aquamapsCurrentRev/revAqNow.shp",append=FALSE)

### crop future data to Revillagigedo area

# aqRev50<-aq50%>%
#   filter(CenterLong>as.numeric(ploArea$xmin),
#          CenterLong<as.numeric(ploArea$xmax),
#          CenterLat>as.numeric(ploArea$ymin),
#          CenterLat<as.numeric(ploArea$ymax))%>%
#   st_as_sf(coords=c("CenterLong","CenterLat"),
#            crs=4326)
# 
# st_write(aqRev50,"data/aquamaps2050Rev/revAq2050.shp",append=FALSE)

```

### Changes to species richness

```{r}

aqRev<-read_sf("data/aquamapsCurrentRev/revAqNow.shp")
aqRev50<-read_sf("data/aquamaps2050Rev/revAq2050.shp")
aqSpp<-read_csv("data/speciesoccursum.csv")

revSR<-aqRev%>%
  mutate(geomID=as.character(geometry))%>%
  group_by(geomID)%>%
  summarise(speciesRich=n())

revSR50<-aqRev50%>%
  mutate(geomID=as.character(geometry))%>%
  group_by(geomID)%>%
  summarise(speciesRich=n())

revSRdiff<-revSR%>%
  rename(srNow=speciesRich)%>%
  st_join(.,revSR50)%>%
  mutate(srDiff=speciesRich-srNow,
         lon=st_coordinates(.)[,1],
           lat=st_coordinates(.)[,2])
  
```

```{r}

sppRichRev<-ggplot()+
  geom_tile(data=revSRdiff,aes(x=lon,y=lat,fill=srDiff),width=0.5,height=0.5)+
  scale_fill_gradient2(low = "#0a6165",high = "#da4325",mid = "#e7e1bc",midpoint = 0,name="Difference in\n# of spp")+
  geom_sf(data=revShp,fill=NA)+
  geom_sf(data=mxShp)+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0),limits = c(ploArea$ymin,ploArea$ymax+0.1))+
  labs(title="Changes in species richness (2019 to 2050)", subtitle = "Data source: Aquamaps",x="longitude",y="latitude")+
  theme_bw()
  
sppRichRev

```

#### Applying thresholds to species presence in richness calculations

Below tests several threshold levels and compares them

**Thresholds tested:**

* 0.4
* 0.5
* 0.6
* 0.7

```{r}

thrsh<-c(0.4,0.5,0.6,0.7)

thrshDf<-revSRdiff%>%
  select(srNow,speciesRich,srDiff,lon,lat)

for(i in 1:length(thrsh)){
  
  colnm<-paste("srDiff",3+i,sep="")
  
  tmpSR<-aqRev%>%
    filter(Probability >= thrsh[i])%>%
    mutate(geomID=as.character(geometry))%>%
    group_by(geomID)%>%
    summarise(sr=n())%>%
    select(-geomID)

  tmpSR50<-aqRev50%>%
    filter(Probability >= thrsh[i])%>%
    mutate(geomID=as.character(geometry))%>%
    group_by(geomID)%>%
    summarise(sr50=n())%>%
    select(-geomID)

  tmpSRdiff<-tmpSR%>%
    st_join(.,tmpSR50)%>%
    mutate(!!colnm := sr50-sr)%>%
    select(-c(sr,sr50))
  
  thrshDf<-thrshDf%>%
    st_join(.,tmpSRdiff)
  
}


```

```{r}

sppRichRev4<-ggplot()+
  geom_tile(data=thrshDf,aes(x=lon,y=lat,fill=srDiff5),width=0.5,height=0.5)+
  scale_fill_gradient2(low = "#0a6165",high = "#da4325",mid = "#e7e1bc",midpoint = 0,name="Difference in\n# of spp")+
  geom_sf(data=revShp,fill=NA)+
  geom_sf(data=mxShp)+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0),limits = c(ploArea$ymin,ploArea$ymax+0.1))+
  labs(title="Changes in species richness (2019 to 2050)", subtitle = "Data source: Aquamaps, 0.4 threshold",x="longitude",y="latitude")+
  theme_bw()
  
sppRichRev4

sppRichRev5<-ggplot()+
  geom_tile(data=thrshDf,aes(x=lon,y=lat,fill=srDiff5),width=0.5,height=0.5)+
  scale_fill_gradient2(low = "#0a6165",high = "#da4325",mid = "#e7e1bc",midpoint = 0,name="Difference in\n# of spp")+
  geom_sf(data=revShp,fill=NA)+
  geom_sf(data=mxShp)+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  labs(title="Changes in species richness (2019 to 2050)", subtitle = "Data source: Aquamaps, 0.5 threshold",x="longitude",y="latitude")+
  theme_bw()
  
sppRichRev5

sppRichRev6<-ggplot()+
  geom_tile(data=thrshDf,aes(x=lon,y=lat,fill=srDiff6),width=0.5,height=0.5)+
  scale_fill_gradient2(low = "#0a6165",high = "#da4325",mid = "#e7e1bc",midpoint = 0,name="Difference in\n# of spp")+
  geom_sf(data=revShp,fill=NA)+
  geom_sf(data=mxShp)+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0),limits = c(ploArea$ymin,ploArea$ymax+0.1))+
  labs(title="Changes in species richness (2019 to 2050)", subtitle = "Data source: Aquamaps, 60% threshold",x="longitude",y="latitude")+
  theme_bw()
  
sppRichRev6

sppRichRev7<-ggplot()+
  geom_tile(data=thrshDf,aes(x=lon,y=lat,fill=srDiff7),width=0.5,height=0.5)+
  scale_fill_gradient2(low = "#0a6165",high = "#da4325",mid = "#e7e1bc",midpoint = 0,name="Difference in\n# of spp")+  
  geom_sf(data=revShp,fill=NA)+
  geom_sf(data=mxShp)+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  labs(title="Changes in species richness (2019 to 2050)", subtitle = "Data source: Aquamaps, 0.7 threshold",x="longitude",y="latitude")+
  theme_bw()
  
sppRichRev7

```

### Invasions and losses from the MPA

```{r}

spLs<-aqRev%>%
  filter(Probability>=0.6)%>% # 50% probability threshold
  st_crop(revShp)%>%
  group_by(SpeciesID)%>%
  summarise(howComm=sum(Probability))%>%
  # select(SpecsID)%>%
  st_drop_geometry()

spLs50<-aqRev50%>%
  filter(Probability>=0.6)%>% # 50% probability threshold
  st_crop(revShp)%>%
  group_by(SpeciesID)%>%
  summarise(howComm50=sum(Probability))%>%
  # select(SpecsID)%>%
  st_drop_geometry()

revSpLoss<-anti_join(spLs,spLs50)%>%
  # rename(SpeciesID=SpecsID)%>%
  left_join(.,aqSpp%>%
              select(SpeciesID, Genus, Species,FBname))%>%
  arrange(desc(howComm))

revSpGain<-anti_join(spLs50,spLs)%>%
  # rename(SpeciesID=SpecsID)%>%
  left_join(.,aqSpp%>%
              select(SpeciesID, Genus, Species,FBname))%>%
  arrange(desc(howComm50))

revSpShifts<-revSpLoss%>%
  mutate(direction="lost")%>%
  bind_rows(.,revSpGain%>%
              rename(howComm=howComm50)%>%
              mutate(direction="intro"))
# write_csv(revSpShifts,"revAqmapSppShifts_thresh50.csv")  

```


### Economically relevant species

Quick look at fishing in the area on the [Global Fishing Water data portal](https://globalfishingwatch.org/map/fishing-activity/udw-revillagigedo_mpa-public?latitude=17.32905138377592&longitude=-111.75727212017733&zoom=5.398953867584273&start=2021-06-13T00%3A00%3A00.000Z&end=2022-06-13T00%3A00%3A00.000Z&bivariateDataviews[0]=fishing-ais&bivariateDataviews[1]=vms&dvIn[0][id]=highlight-sar-match&dvIn[0][cfg][vis]=false&dvIn[1][id]=viirs&dvIn[1][cfg][vis]=false&dvIn[2][id]=presence&dvIn[2][cfg][vis]=false) shows that *tuna purse seining* is the main fishing gear in the area. This gear target tuna and mackerel species, which fall into one of the following genus':

```{r}

tunMacs<-data.frame(genus=c("Thunnus","Neothunnus","Allothunnus","Auxis","Euthynnus","Katsuwonus","Rastrelliger","Scomber","Acanthocybium","Grammatorcynus","Scomberomorus"),
                    fish=c(rep("tuna",6),rep("mackerel",5)))

kable(tunMacs)

```

```{r}

fishedChg<-revSpShifts%>%
  filter(Genus %in% tunMacs$genus)
# write_csv(fishedChg,"outputs/revSpShft_tunas.csv")
kable(fishedChg)

```

#### What's going to happen to these tuna fisheries?

```{r}

tunDist<-aqRev%>%
  mutate(year=2019)%>%
  bind_rows(aqRev50%>%mutate(year=2050))%>%
  mutate(lon=st_coordinates(.)[,1],
           lat=st_coordinates(.)[,2])%>%
  filter(SpeciesID %in% fishedChg$SpeciesID)

```

```{r}


tun1n<-tunDist%>%
  filter(SpeciesID == fishedChg$SpeciesID[1],
         year==2019)%>%
  ggplot()+
   geom_tile(aes(x=lon,y=lat,fill=Probability),width=0.5,height=0.5)+
  scale_fill_gradient(name="Probability of\noccurance",limits=c(0,1),low="white",high="orangered4")+
  geom_sf(data=revShp,fill=NA)+
  geom_sf(data=mxShp)+
  scale_x_continuous(limits=c(ploArea$xmin,ploArea$xmax),expand=c(0,0))+
  scale_y_continuous(limits=c(ploArea$ymin,ploArea$ymax),expand=c(0,0))+
  labs(title="Friget Tuna", subtitle = "2019",x="longitude",y="latitude")+
  theme_bw()

tun1f<-tunDist%>%
  filter(SpeciesID == fishedChg$SpeciesID[1],
         year==2050)%>%
  ggplot()+
   geom_tile(aes(x=lon,y=lat,fill=Probability),width=0.5,height=0.5)+
  scale_fill_gradient(name="Probability of\noccurance",limits=c(0,1),low="white",high="orangered4")+
  geom_sf(data=revShp,fill=NA)+
  geom_sf(data=mxShp)+
  scale_x_continuous(limits=c(ploArea$xmin,ploArea$xmax),expand=c(0,0))+
  scale_y_continuous(limits=c(ploArea$ymin,ploArea$ymax),expand=c(0,0))+
  labs(title="\n", subtitle = "2050",x="longitude",y="latitude")+
  theme_bw()

tun1n+tun1f+plot_layout(guides = "collect")

```

```{r}


tun2n<-tunDist%>%
  filter(SpeciesID == fishedChg$SpeciesID[2],
         year==2019)%>%
  ggplot()+
   geom_tile(aes(x=lon,y=lat,fill=Probability),width=0.5,height=0.5)+
  scale_fill_gradient(name="Probability of\noccurance",limits=c(0,1),low="white",high="orangered4")+
  geom_sf(data=revShp,fill=NA)+
  geom_sf(data=mxShp)+
  scale_x_continuous(limits=c(ploArea$xmin,ploArea$xmax),expand=c(0,0))+
  scale_y_continuous(limits=c(ploArea$ymin,ploArea$ymax),expand=c(0,0))+
  labs(title="Black skipjack", subtitle = "2019",x="longitude",y="latitude")+
  theme_bw()

tun2f<-tunDist%>%
  filter(SpeciesID == fishedChg$SpeciesID[2],
         year==2050)%>%
  ggplot()+
   geom_tile(aes(x=lon,y=lat,fill=Probability),width=0.5,height=0.5)+
  scale_fill_gradient(name="Probability of\noccurance",limits=c(0,1),low="white",high="orangered4")+
  geom_sf(data=revShp,fill=NA)+
  geom_sf(data=mxShp)+
  scale_x_continuous(limits=c(ploArea$xmin,ploArea$xmax),expand=c(0,0))+
  scale_y_continuous(limits=c(ploArea$ymin,ploArea$ymax),expand=c(0,0))+
  labs(title="\n", subtitle = "2050",x="longitude",y="latitude")+
  theme_bw()

tun2n+tun2f+plot_layout(guides = "collect")

```

```{r}


tun3n<-tunDist%>%
  filter(SpeciesID == fishedChg$SpeciesID[3],
         year==2019)%>%
  ggplot()+
   geom_tile(aes(x=lon,y=lat,fill=Probability),width=0.5,height=0.5)+
  scale_fill_gradient(name="Probability of\noccurance",limits=c(0,1),low="white",high="orangered4")+
  geom_sf(data=revShp,fill=NA)+
  geom_sf(data=mxShp)+
  scale_x_continuous(limits=c(ploArea$xmin,ploArea$xmax),expand=c(0,0))+
  scale_y_continuous(limits=c(ploArea$ymin,ploArea$ymax),expand=c(0,0))+
  labs(title="Chub mackerel", subtitle = "2019",x="longitude",y="latitude")+
  theme_bw()

tun3f<-tunDist%>%
  filter(SpeciesID == fishedChg$SpeciesID[3],
         year==2050)%>%
  ggplot()+
   geom_tile(aes(x=lon,y=lat,fill=Probability),width=0.5,height=0.5)+
  scale_fill_gradient(name="Probability of\noccurance",limits=c(0,1),low="white",high="orangered4")+
  geom_sf(data=revShp,fill=NA)+
  geom_sf(data=mxShp)+
  scale_x_continuous(limits=c(ploArea$xmin,ploArea$xmax),expand=c(0,0))+
  scale_y_continuous(limits=c(ploArea$ymin,ploArea$ymax),expand=c(0,0))+
  labs(title="\n", subtitle = "2050",x="longitude",y="latitude")+
  theme_bw()

tun3n+tun3f+plot_layout(guides = "collect")

```

```{r}


tun4n<-tunDist%>%
  filter(SpeciesID == fishedChg$SpeciesID[4],
         year==2019)%>%
  ggplot()+
   geom_tile(aes(x=lon,y=lat,fill=Probability),width=0.5,height=0.5)+
  scale_fill_gradient(name="Probability of\noccurance",limits=c(0,1),low="white",high="orangered4")+
  geom_sf(data=revShp,fill=NA)+
  geom_sf(data=mxShp)+
  scale_x_continuous(limits=c(ploArea$xmin,ploArea$xmax),expand=c(0,0))+
  scale_y_continuous(limits=c(ploArea$ymin,ploArea$ymax),expand=c(0,0))+
  labs(title="Pacific sierra", subtitle = "2019",x="longitude",y="latitude")+
  theme_bw()

tun4f<-tunDist%>%
  filter(SpeciesID == fishedChg$SpeciesID[4],
         year==2050)%>%
  ggplot()+
   geom_tile(aes(x=lon,y=lat,fill=Probability),width=0.5,height=0.5)+
  scale_fill_gradient(name="Probability of\noccurance",limits=c(0,1),low="white",high="orangered4")+
  geom_sf(data=revShp,fill=NA)+
  geom_sf(data=mxShp)+
  scale_x_continuous(limits=c(ploArea$xmin,ploArea$xmax),expand=c(0,0))+
  scale_y_continuous(limits=c(ploArea$ymin,ploArea$ymax),expand=c(0,0))+
  labs(title="\n", subtitle = "2050",x="longitude",y="latitude")+
  theme_bw()

tun4n+tun4f+plot_layout(guides = "collect")

```

***

### Species turnover

```{r}

library(codyn) # turnover() below errored on something that didnt make sense (referencing data that isn't used in the call)so instead of troubleshooting I just tried calculating manually
library(betapart)

### calculate turnover using the codyn package

sppLst<-bind_rows(aqRev,aqRev50)%>%
  select(SpecsID)%>%
  filter(!duplicated(SpecsID))%>%
  st_drop_geometry()

revTurn<-sppLst%>%
  left_join(.,aqRev)%>%
  # filter(Prbblty>=0.6)%>%
  mutate(coords=as.character(geometry),
         pres=case_when(Prbblty>0.5 ~ 1,
                        TRUE ~ 0),
         pres=as.numeric(pres))%>%
  select(-Prbblty)%>%
  pivot_wider(names_from = SpecsID,values_from = pres)#%>%
  # select(-c(coords))

revTurn[is.na(revTurn)] <- 0 
    
revTurn50<-sppLst%>%
  left_join(.,aqRev50)%>%
  # filter(Prbblty>=0.6)%>%
  mutate(coords=as.character(geometry),
         pres=case_when(Prbblty>0.5 ~ 1,
                        TRUE ~ 0),
         pres=as.numeric(pres))%>%
  select(-c(geometry,Prbblty))%>%
  pivot_wider(names_from = SpecsID,values_from = pres)#%>%
  # select(-c(coords))

revTurn50[is.na(revTurn50)] <- 0 

### codyn
# turnovrRev <- turnover(df=revTurn,
#                     time.var = "year",
#                     species.var = "SpecsID",
#                     abundance.var = "Prbblty",
#                     replicate.var = "coords",
#                     metric = "total")
  

```

```{r}

### betpart
turnovrRev<-beta.temp(x=revTurn%>%select(-c(geometry,coords)),
                      y=revTurn50%>%select(-c(coords))) ### sorensen

turnRev<-bind_cols(revTurn%>%select(geometry),turnovrRev)%>%
  st_as_sf(crs = st_crs(revShp))%>%
  mutate(lon=st_coordinates(.)[,1],
           lat=st_coordinates(.)[,2])

toRevPlt<-turnRev%>%
  ggplot()+
  geom_tile(aes(x=lon,y=lat,fill=beta.sim))+
  scale_fill_gradient(name="Dissimilarity/turnover",limits=c(0,1),low="white",high="orangered4")+
  geom_sf(data=revShp,fill=NA)+
  geom_sf(data=mxShp)+
  scale_x_continuous(limits=c(ploArea$xmin,ploArea$xmax),expand=c(0,0))+
  scale_y_continuous(limits=c(ploArea$ymin,ploArea$ymax),expand=c(0,0))+
  labs(title="Species Turnover", subtitle = "Between 2019 and 2050",x="",y="Sorensen\nlatitude")+
  theme_bw()

# toRevPlt

```

```{r}
toTotRevPlt<-turnRev%>%
  ggplot()+
  geom_tile(aes(x=lon,y=lat,fill=beta.sor))+
  scale_fill_gradient(name="Dissimilarity/turnover",limits=c(0,1),low="white",high="orangered4")+
  geom_sf(data=revShp,fill=NA)+
  geom_sf(data=mxShp)+
  scale_x_continuous(limits=c(ploArea$xmin,ploArea$xmax),expand=c(0,0))+
  scale_y_continuous(limits=c(ploArea$ymin,ploArea$ymax),expand=c(0,0))+
  labs(title="Total Species Dissimilarity", subtitle = "Between 2019 and 2050",x="",y="latitude")+
  theme_bw()

# toTotRevPlt


```


```{r}

### betpart
turnovrRevJac<-beta.temp(x=revTurn%>%select(-c(geometry,coords)),
                      y=revTurn50%>%select(-c(coords)),
                      index.family = "jaccard") ### Jaccard

turnRevJ<-bind_cols(revTurn%>%select(geometry),turnovrRevJac)%>%
  st_as_sf(crs = st_crs(revShp))%>%
  mutate(lon=st_coordinates(.)[,1],
           lat=st_coordinates(.)[,2])

toRevJPlt<-turnRevJ%>%
  ggplot()+
  geom_tile(aes(x=lon,y=lat,fill=beta.jtu))+
  scale_fill_gradient(name="Dissimilarity/turnover",limits=c(0,1),low="white",high="orangered4")+
  geom_sf(data=revShp,fill=NA)+
  geom_sf(data=mxShp)+
  scale_x_continuous(limits=c(ploArea$xmin,ploArea$xmax),expand=c(0,0))+
  scale_y_continuous(limits=c(ploArea$ymin,ploArea$ymax),expand=c(0,0))+
  labs(title="Species Turnover", subtitle = "Between 2019 and 2050",x="longitude",y="latitude")+
  theme_bw()

# toRevJPlt

```


```{r}

toTotRevJPlt<-turnRevJ%>%
  ggplot()+
  geom_tile(aes(x=lon,y=lat,fill=beta.jac))+
  scale_fill_gradient(name="Dissimilarity/turnover",limits=c(0,1),low="white",high="orangered4")+
  geom_sf(data=revShp,fill=NA)+
  geom_sf(data=mxShp)+
  scale_x_continuous(limits=c(ploArea$xmin,ploArea$xmax),expand=c(0,0))+
  scale_y_continuous(limits=c(ploArea$ymin,ploArea$ymax),expand=c(0,0))+
  labs(title="Total Species Dissimilarity",subtitle = "Between 2019 and 2050",x="longitude",y="")+
  theme_bw()

# toTotRevJPlt

```

```{r}

toRevPlt + toTotRevPlt + toRevJPlt + toTotRevJPlt + plot_layout(guides = "collect")

```

```{r}
toRevJPlt + toTotRevJPlt + plot_layout(guides = "collect")

```

